manuscript_figures

### 2024-05-24 scripts/manuscript_figures.Rmd
making figure 2

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(patchwork)
```

@@

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

```
# Make Figure 2

```{r}

# Aggregate the data by year, site, and transect and compute mean values
aggregated_data <- merged.dat %>%
  group_by(year, site, transect) %>%
  summarize(mean_fish_biomass = mean(fish_biomass, na.rm = TRUE),
            mean_kelp_cover = mean(kelp_cover, na.rm = TRUE)) %>%
  ungroup()

# Perform linear regression
lm_model <- lm(mean_fish_biomass ~ mean_kelp_cover, data = aggregated_data)
lm_summary <- tidy(lm_model)

# Create scatter plot
scatter_plot <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  geom_text(data = lm_summary, aes(label = paste("R² =", round(r.squared, 2), ", p =", signif(p.value, 2))),
            x = Inf, y = Inf, hjust = 1, vjust = 1, size = 4, parse = TRUE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover",
       caption = "Linear regression with 95% CI bands") +
  theme_minimal()

# Display the plot
print(scatter_plot)
